DATA 621 Week #2 Textbook Exercises

### 2019-09-06 DATA621/Week 2 Textbook Exercises.Rmd
More work

>>>>

The web site www.playbill.com provides weekly reports on the box office ticket sales for plays on Broadway in New York.  We shall consider the data for the week Octover 11-17, 2004 (reffered to below as the current week).  The data are in the form of the gross box office results for the current week and the gross box office results for the previous wek (i.e., October 3-10, 2004).

Fit the following model to the data: $Y=\beta_0 + \beta_1 x + e$ where $Y$ is the gross box office results for the current week (in $) and $x$ is the gross box office results for the previous week (in $).  Compleete the following tasks:

```{r, comment=NA}
playbill <- read.csv("data/playbill.csv")
# teengamb <- read.delim("data/teengamb.txt") %>%
#   mutate(sex = as.factor(ifelse(sex == 0, "Male", "Female")))
fit <- lm(CurrentWeek ~ LastWeek, data = playbill)
summary(fit)
```

A. Find a 95% confidence interval for the slope of the regression model, $\beta_1$.  Is 1 a plausible value for $\beta_1$?  Give a reason to support your answer.

```{r, null_prefix=TRUE}
confint(fit, "LastWeek")
```

**Yes.  It is plausible because it falls within the range of the 95% confidence interval.**

B. Test the null hypothesis $H_0 : \beta_0 = 10000$ against a two-sided alternative.  Interpret your result.
